### 2007-09-06 doc/a-rex/arex_tech_doc.tex
Updating a-rex document according to some of comments from Adrian.

{\raggedleft NORDUGRID-TECH-2\par}

@@

Each job is initiated and controlled through GFS or WS. All job parameters
(not data) are passed to the GM through GFS in RSL \cite{rsl} or
through WS in JSDL-coded \cite{jsdl} description (job description
- JD).

@@

A-REX Web Service Specific Interface provides means to submit a description
of a computational job to a computing resource, to stage-in additional
data, to monitor and control processing of jobs, and obtain data produced
during the execution of a job.

@@

\begin{itemize}
\item \emph{ActivityStatusType OldStatus}: Description of the state which
the job is supposed to be in during execution of this request. If
the current state of the job is different from the one having been
given, the operation is aborted and a fault is returned. This parameter
is optional.
\item \emph{ActivityStatusType NewStatus}: Description of the state that
the job is to be put into.
\end{itemize}
\item Output

@@

\begin{itemize}
\item \emph{DelegateCredentialsInit} operation - this operation performs
the first half of credentials delegation sequence.

@@

\begin{itemize}
\item \emph{DelegatedTokenType DelegatedToken}: Contains an X509 proxy certificate
based on the public key from the DelegateCredentialsInit signed by
the user?s proxy certificate. Also includes the Id element which identifies
the private key stored at the service side associated with these credentials.
Reference element refers to the object which these credentials should
be applied to in a way specific to the service. The same element must
also be used for delegating credentials as part of other operations
on service.
\end{itemize}
\item Output(s)

@@

\begin{lyxlist}{00.00.0000}
\item [{\emph{BESFactory}}] collection of BES Factory attributes as defined
in the BES specifications.
\item [{\emph{Glue2Resource}}] description of a computation resource that
uses Glue2 schema. This one is going to be specified after the Glue2
XML bindings are be available.
\item [{\emph{Activities}}] list of maintained activities. Each activity
contains an identifier (\emph{ActivityIdentifier}), BES (\emph{ActivityDocument})
and Glue2 (\emph{Glue2Job}) descriptions of the activity.
\end{lyxlist}
All information can be accessed either through requests on a particular
resources or through XPath queries using WS-Resource Properties operations.

@@

\begin{lyxlist}{00.00.0000}
\item [{\emph{JobName}}] name of the job as assigned by the user.
\item [{\emph{Executable}\ (POSIX)}] name of the executable file.
\item [{\emph{Argument}\ (POSIX)}] arguments the executable will be launched
with.
\item [{\emph{DataStaging}}]~

\begin{lyxlist}{00.00.0000}
\item [{Filename}] name of the data file on the executing node.
\item [{\emph{Source}}] source where the file will be taken from before
execution.
\item [{\emph{Target}}] destination the file will be delivered to after
execution.
\end{lyxlist}
\item [{\emph{Input}\,\ (POSIX)}] file to be used as standard input for
the executable.
\item [{\emph{Output}\ (POSIX)}] file to be used as standard output for
the executable.
\item [{\emph{Error}\ (POSIX)}] file to be used as standard error for
the executable.
\item [{\emph{MemoryLimit}\ (POSIX)}] amount of physical memory needed
for execution.
\item [{\emph{TotalPhysicalMemory}}] same as MemoryLimit.
\item [{\emph{IndividualPhysicalMemory}}] same as MemoryLimit.
\item [{\emph{CPUTimeLimit}\ (POSIX)}] maximal amount of CPU time needed
for execution.
\item [{\emph{TotalCPUTime}}] same as CPUTimeLimit.
\item [{\emph{IndividualCPUTime}}] same as CPUTimeLimit.
\item [{\emph{WallTimeLimit}\ (POSIX)}] amount of clock time needed for
execution.
\item [{\emph{TotalCPUCount}}] number of CPUs needed for execution.
\item [{\emph{IndividualCPUCount}}] same as TotalCPUCount.
\end{lyxlist}

@@

\begin{lyxlist}{00.00.0000}
\item [{\emph{IsExecutable}}] marks file to become executable after being
delivered to the computing resource.
\item [{\emph{RunTimeEnvironment}}] specifies the name of the Runtime Environment
needed for job execution.
\item [{\emph{Middleware}}] request for specific middleware on the computing
resource frontend.
\item [{\emph{RemoteLogging}}] destination for the usage record report
of the executed job.
\item [{\emph{LocalLogging}}] name for the virtual directory available
through job interface and containing various debug information about
job execution.
\item [{\emph{AccessControl}}] ACL expression which describes the identities
of those clients who are allowed to perform operations on this job.
\item [{\emph{Notify}}] Email destination for notification of job state
changes.
\item [{\emph{SessionLifeTime}}] duration for the directory containing
job-related files to exist after the job finished executing.
\item [{\emph{JoinOutputs}}] specifies if standard output and standard
error channels must be merged.
\item [{\emph{Reruns}}] defines how many times a job is allowed to rerun
in case of failure.
\item [{\emph{CredentialServer}}] URL of MyProxy service which may be used
for renewing the expired delegated job credentials.
\item [{\emph{CandidateTarget}}] specifies host name and queue of a computing
resource.
\end{lyxlist}

@@

~~~~~~~~~~<xsd:complexType~name=?Glue2Resource?~minOccurs='0'>

@@

~~~~~~~~~~~~~~~~~~<xsd:element~ref=?bes-factory:ActivityDocument?~minOccurs='0'/>

~~~~~~~~~~~~~~~~~~<xsd:complexType~name=?Glue2Job?~minOccurs='0'>

@@

>>>>

{\raggedleft NORDUGRID-TECH-14\par}

@@

Each job is initiated and controlled through GFS or WS. Complete description
of job (not data) is passed to the GM through GFS in RSL \cite{rsl}
or through WS in JSDL-coded \cite{jsdl} description (job description
- JD).

@@

A-REX Web Service Interface provides means to submit a description
of a computational job to a computing resource, to stage-in additional
data, to monitor and control processing of jobs, and obtain data produced
during the execution of a job. The WS Interface is built and deployed
inside Hosting Envirnoment Daemon {[}HED] infrastructure\cite{hed}.

@@

\begin{itemize}
\item \emph{ActivityStatusType OldStatus}: Description of the state the
job is supposed to be in during execution of this request. If the
current state of the job is different from the one having been given,
the operation is aborted and a fault is returned. This parameter is
optional.
\item \emph{ActivityStatusType NewStatus}: Description of the state the
job is to be put into.
\end{itemize}
\item Output

@@

\begin{itemize}
\item \emph{DelegateCredentialsInit} operation - this operation performs
the first half of the credentials delegation sequence.

@@

\begin{itemize}
\item \emph{DelegatedTokenType DelegatedToken}: Contains an X509 proxy certificate
based on the public key from the DelegateCredentialsInit signed by
the user's proxy certificate. Also includes the Id element which identifies
the private key stored at the service side associated with these credentials.
The reference element refers to the object which these credentials
should be applied to in a way specific to the service. The same element
must also be used for delegating credentials as part of other operations
on service.
\end{itemize}
\item Output(s)

@@

\begin{lyxlist}{00.00.0000}
\item [{\emph{BESFactory}}] - collection of BES Factory attributes as defined
in the BES specifications.
\item [{\emph{Glue2Resource}}] \emph{-} description of a computation resource
that uses Glue2 schema. This one is going to be specified after the
Glue2 XML bindings will be available.
\item [{\emph{Activities}}] \emph{-} list of maintained activities. Each
activity contains an identifier (\emph{ActivityIdentifier}), BES (\emph{ActivityDocument})
and Glue2 (\emph{Glue2Job}) descriptions of the activity.
\end{lyxlist}
All information can be accessed either through requests on particular
resources or through XPath queries using WS-Resource Properties operations.

@@

\begin{lyxlist}{00.00.0000}
\item [{\emph{JobName}}] \emph{-} name of the job as assigned by the user.
\item [{\emph{Executable}\ (POSIX)}] - name of the executable file.
\item [{\emph{Argument}\ (POSIX)}] - arguments the executable will be
launched with.
\item [{\emph{DataStaging}}]~

\begin{lyxlist}{00.00.0000}
\item [{Filename}] - name of the data file on the executing node.
\item [{\emph{Source}}] - source where the file will be taken from before
execution.
\item [{\emph{Target}}] \emph{-} destination the file will be delivered
to after execution.
\end{lyxlist}
\item [{\emph{Input}\,\ (POSIX)}] - file to be used as standard input
for the executable.
\item [{\emph{Output}\ (POSIX)}] - file to be used as standard output
for the executable.
\item [{\emph{Error}\ (POSIX)}] - file to be used as standard error for
the executable.
\item [{\emph{MemoryLimit}\ (POSIX)}] - amount of physical memory needed
for execution.
\item [{\emph{TotalPhysicalMemory}}] - same as MemoryLimit.
\item [{\emph{IndividualPhysicalMemory}}] - same as MemoryLimit.
\item [{\emph{CPUTimeLimit}\ (POSIX)}] - maximal amount of CPU time needed
for execution.
\item [{\emph{TotalCPUTime}}] - same as CPUTimeLimit.
\item [{\emph{IndividualCPUTime}}] - same as CPUTimeLimit.
\item [{\emph{WallTimeLimit}\ (POSIX)}] - amount of clock time needed
for execution.
\item [{\emph{TotalCPUCount}}] \emph{-} number of CPUs needed for execution.
\item [{\emph{IndividualCPUCount}}] - same as TotalCPUCount.
\end{lyxlist}

@@

\begin{lyxlist}{00.00.0000}
\item [{\emph{IsExecutable}}] \emph{-} marks file to become executable
after being delivered to the computing resource.
\item [{\emph{RunTimeEnvironment}}] - specifies the name of the Runtime
Environment needed for job execution.
\item [{\emph{Middleware}}] - request for specific middleware on the computing
resource frontend.
\item [{\emph{RemoteLogging}}] \emph{-} destination for the usage record
report of the executed job.
\item [{\emph{LocalLogging}}] - name for the virtual directory available
through job interface and containing various debug information about
job execution.
\item [{\emph{AccessControl}}] - ACL expression which describes the identities
of those clients who are allowed to perform operations on this job.
\item [{\emph{Notify}}] - Email destination for notification of job state
changes.
\item [{\emph{SessionLifeTime}}] - duration for the directory containing
job-related files to exist after the job finished executing.
\item [{\emph{JoinOutputs}}] - specifies if standard output and standard
error channels must be merged.
\item [{\emph{Reruns}}] \emph{-} defines how many times a job is allowed
to rerun in case of failure.
\item [{\emph{CredentialServer}}] \emph{-} URL of MyProxy service which
may be used for renewing the expired delegated job credentials.
\item [{\emph{CandidateTarget}}] \emph{-} specifies host name and queue
of a computing resource.
\end{lyxlist}

@@

~~~~~~~~~~<xsd:complexType~name=\char`\"{}Glue2Resource\char`\"{}~minOccurs='0'>

@@

~~~~~~~~~~~~~~~~~~<xsd:element~ref=\char`\"{}bes-factory:ActivityDocument\char`\"{}~minOccurs='0'/>

~~~~~~~~~~~~~~~~~~<xsd:complexType~name=\char`\"{}Glue2Job\char`\"{}~minOccurs='0'>

@@

~~~~~~<wsdl:fault~name=\char`\"{}NotAuthorizedFault\char`\"{}>

~~~~~~~~<soap:fault~name=\char`\"{}NotAuthorizedFault\char`\"{}~use=\char`\"{}literal\char`\"{}~/>

~~~~~~<wsdl:fault~name=\char`\"{}InvalidActivityIdentifierFault\char`\"{}>

~~~~~~~~<soap:fault~name=\char`\"{}InvalidActivityIdentifierFault\char`\"{}~use=\char`\"{}literal\char`\"{}~/>

~~~~~~<wsdl:fault~name=\char`\"{}CantApplyOperationToCurrentStateFault\char`\"{}>

~~~~~~~~<soap:fault~name=\char`\"{}CantApplyOperationToCurrentStateFault\char`\"{}~use=\char`\"{}literal\char`\"{}~/>

~~~~~~<wsdl:fault~name=\char`\"{}OperationWillBeAppliedEventuallyFault\char`\"{}>

~~~~~~~~<soap:fault~name=\char`\"{}OperationWillBeAppliedEventuallyFault\char`\"{}~use=\char`\"{}literal\char`\"{}~/>
